\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}
\overfullrule=0pt
\usepackage[colorlinks=false,draft=false]{hyperref}

\usepackage{xcolor}
% \usepackage{verbatim}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\definecolor{blue}{HTML}{005cc5}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\renewcommand\fbox{\fcolorbox{red}{white}}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheadingBold}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{\small#1} & \textbf{}{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Rishabh Malhotra} \\ \vspace{3pt}
    % 123 Street Name, Town, State 12345 \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +91-8851958205 ~ \href{mailto:rmalhotra_be18@thapar.edu}{\raisebox{-0.2\height}\faEnvelope\  \underline{rmalhotra\_be18@thapar.edu}} ~ 
    \href{https://linkedin.com/in/rishabh-malhotra-4536a418b/}{\raisebox{-0.2\height}\faLinkedin\ \underline{rishabh-malhotra}}  ~
    \href{https://github.com/Rishabh-malhotraa}{\raisebox{-0.2\height}\faGithub\ \underline{Rishabh-malhotraa}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Thapar Institute of Engineering And Technology}{May 2018 -- May 2022}
      {B.E. Computer Engineering - Major Elective - Graph Theory}{Patiala, Punjab}
  \resumeSubHeadingListEnd

% %------RELEVANT COURSEWORK-------
% \section{Relevant Coursework}
%     %\resumeSubHeadingListStart
%         \begin{multicols}{4}
%             \begin{itemize}[itemsep=-5pt, parsep=3pt]
%                 \item\small Data Structures
%                 \item Software Methodology
%                 \item Algorithms Analysis
%                 \item Database Management
%                 \item Artificial Intelligence
%                 \item Internet Technology
%                 \item Systems Programming
%                 \item Computer Architecture
%             \end{itemize}
%         \end{multicols}
%         \vspace*{2.0\multicolsep}
%     %\resumeSubHeadingListEnd



%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Caucus : A real time collaborative editor} $|$ \emph{Typescript, React, NodeJS, Webrtc, PostgreSQL }}{May'21}
          \resumeItemListStart
            \resumeItem{\href{https://caucus-app.herokuapp.com/}{\color{blue} {\underline{Caucus}}} is a real-time collaborative editor with an embedded compiler that helps students practice for online coding interviews.}
            \resumeItem{Accomplished real-time collaboration using Webrtc and CRDT (\emph{Conflict free Replicated Data Type}) and chat functionality with the help of web-sockets.}
            \resumeItem{Implemented user authorization using OAuth 2.0 protocol with passport library in NodeJS.}
            \resumeItem{Uses CRDT's for conflict resolution while merging two documents while two people are collaborating.}
            \resumeItem{Incorporated remote code execution, enabling users to compile \& run code in C++, Java, Python, JavaScript, Golang \& Rust.}
            \resumeItem{Gathered over \fbox{\textbf{160 stars}} on \href{https://github.com/Rishabh-malhotraa/caucus}{ \color{blue} \underline{{GitHub}}} with over \textbf{1000} registered users, and \fbox{\textbf{40000+}} website visits.}
          \resumeItemListEnd
          \vspace{-13pt}
        %   CODE FORCES DIARY PROJECT
      \resumeProjectHeading
          {\textbf{Code Forces Diary} $|$ \emph{React,  Redux, Typescript}}{Nov'20}
          \resumeItemListStart
             \resumeItem{Developed a \href{https://codeforces-diary.netlify.app/}{ \color{blue} {\underline{website}}} that visualizes user data from codeforces public API into charts and graphs.}
            \resumeItem{Built with React using D3.js library for visualization.}
            \resumeItem{It has gathered over \fbox{\textbf{60 stars}} on \href{https://github.com/Rishabh-malhotraa/codeforces-diary}{ \color{blue} \underline{{GitHub}}} with over \fbox{\textbf{8000+}} website visits.}
          \resumeItemListEnd 
          \vspace{-13pt}
          \resumeProjectHeading
          {\textbf{Leetcode REST API} $|$ \emph{Selenium, Cheerio, NodeJS, Sqlite}}{Mar'21}
          \resumeItemListStart
            \resumeItem{Developed a RESTFUL API in NodeJS which sends Leetcode question data in form of JSON.}
            \resumeItem{Used selenium and cheerio to scrape all the free-questions from the Leetcode website.}
            \resumeItem{Uses Sqlite to store and Knex.js as query-builder to retrieve the list of questions, filtered based on tags, difficulty and company name.}
          \resumeItemListEnd 
                    \vspace{-13pt}
          \resumeProjectHeading
          {\textbf{Data Structure Repository} $|$ \emph{C++, Golang}}{Aug'19 -- Present}
          \resumeItemListStart
            \resumeItem{Documented all the \fbox{\textbf{\textit{500+}}} questions solved on Leetcode, codeforces \& GeeksForGeeks.}
            \resumeItem{Leetcode Profile \ \ \ \ \ \ \ \  \ \ \ : \href{https://leetcode.com/Rishabh-malhotraa/}{ \color{blue} {\underline{leetcode/Rishabh-malhotraa}}}}
            \resumeItem{GeeksForGeeks Profile \ \ \ : \href{https://auth.geeksforgeeks.org/user/rishabh_malhotra/profile}{ \color{blue} {\underline{geeksforgeeks/Rishabh-malhotraa}}}}
            % \resumeItem{GeeksForGeeks Profile : 
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-15pt}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Genpact}{Aug'20 -- Oct'20}
      {Full Stack Developer Intern}{Remote}
      \resumeItemListStart
        \resumeItem{Designed and developed \href{https://crispy-spoon.netlify.app}{\underline{custom form}} to streamline the process of entering data that needs to be analyzed.}
        \resumeItem{Developed a backend in python to handle file upload, normalize and pre-process the data before send it to the spring micro-service.}
        \resumeItem{Built the frontend using React JS Typescript and Material UI and designed UI mockups in Figma.}
      \resumeItemListEnd

    \resumeSubheading
      {Open Source}{Mar'20 -- Present}
      {}{}
      \vspace{-20pt}
      \resumeSubSubheadingBold{\textbf{ \ \ \ \ \ Navidrome} $|$ \emph{Golang, React, Sqlite}}{}
         \resumeItemListStart[leftmargin=+.7in] 
            \resumeItem{Collaborated with the maintainer of the project to add features and remove bugs present in Navidrome, which is written in React and GoLang.}
            \resumeItem{List of \href{https://github.com/navidrome/navidrome/pulls?q=is\%3Apr+author\%3Arishabh-malhotraa}{\underline{Pull Request}} and \href{https://github.com/navidrome/navidrome/issues?q=is\%3Aissue+author\%3ARishabh-malhotraa+}{\underline{Issues}} raised on GitHub for Navidrome.}
          \resumeItemListEnd 
          \resumeSubSubheadingBold{\textbf{ \ \ \ \ \ Joplin} $|$ \emph{Electron, React, Typescript, Sqlite, NodeJS }}{}
          \resumeItemListStart[leftmargin=+.7in] 
            \resumeItem{Worked on the open-source note-taking app \href{https://github.com/laurent22/joplin/pulls?q=author\%3Arishabh-malhotraa}{\underline{Joplin}}, written in electronJS, also made a \href{https://rishabh-malhotraa.github.io/Joplin-proposal-draft/}{\underline{re-imagined inline}} markdown/WYSIWYG editor for Joplin using React. }
            \resumeItem{Improved documentation, and gained first-hand software development experience from the maintainers of the repository.}
          \resumeItemListEnd 
          \resumeItemListEnd 

       \vspace{-8pt}
%
        %-----------PROGRAMMING SKILLS-----------
        \section{Technical Skills}
         \begin{itemize}[leftmargin=0.15in, label={}]
            \normalsize{\item{
             \textbf{Languages}{: JavaScript, TypeScript, GoLang, HTML/CSS, C++, SQL, Python, LaTex} \\
        	 \vspace{4pt}
             \textbf{Developer Tools}{: VS Code, Vim, Git, GitHub, Figma } \\
        	 \vspace{4pt}
             \textbf{Technologies/Frameworks}{: React, Express, Docker, Azure, Nginx, Websockets, Webrtc} \\
            }}
         \end{itemize}
         \vspace{-16pt}

\end{document}
